\chapter{Introduction}

\section{Background}
This project intends to replace the current archaic process of storing health records and the entire insurance policy life cycle i.e. from buying insurance to policy servicing to claim settlement.

The current insurance system has a lot of problems or challenges like there is a lack of trust between the buyer and the seller(insurance company), the user has to manage all his paper based records(for example health records, policy records,etc), a lot of middlemen are involved in the entire process starting from buying a policy to claim settlement.
    
This project addresses the above mentioned problems by helping the users to manage their health records and maintain their medical history. Being a completely digital platform middlemen are eliminated introducing much more transparency in the system. Claim settlements will be quick and easy saving user’s time and efforts.
\section{Aim}
\begin{itemize}
	\item Study the blockchain technology and applying it in solving the problem.
	\item Learn Solidity contract oriented programming language to write smart contracts.
	\item Learn to create nodes and deploy the blockchain network on Microsoft Azure Platform.
	\item 	Understand and learn the React.js library for building user interfaces.
\end{itemize}
     
\section{Goals}
\begin{itemize}
	\item To create an efficient and streamlined healthcare system.
	\item Secured storage and sharing of medical records.
	\item	Ensure structural interoperability between healthcare centers.
	\item Easier to track medical history.
	\item Reduce middlemen involved in the insurance policy life cycle.
	\item Reduce manpower and interactions required in claim verification.
	\item Facilitate automated and quick claim settlement by using Smart Contracts
\end{itemize}
\section{Software Development Model}
The project has four major use-cases: Identity Management, Uploading Health Records,Policy Servicing and Claim Settlement. The software is built one use-case after another.The first version is not the final version, it is like a test version which will give user the feel of the system.The use-cases are refined and more functionality is added in each iteration of refinement. The software development model used here is Incremental Model. The requirements of the software are all set in the beginning and in every iteration a new functionality is added or modified.
    
\section{Report Overview}
This report consists of the following details related to the project-
\begin{itemize}
	\item Background and Literature Review: This section describes the current scenario or system related to this project, the survey of existing solutions similar to this project, a description of the project work carried out to learn about the methodology used for the investigation of the problem, key sources of information(like research papers,etc.) and the tools and technologies being used to implement this project.
	\item 	Requirement and Analysis: This section focuses on the intricate details of the project which includes the problem statement, the requirements specifications, system features, involved parties in the system, use-cases in the project, software and hardware related details of this project.
	\item  Design: This section covers the design details of the project. It includes the system architecture, UML diagrams - use-case diagram, class diagram, activity diagram, sequence diagram which will explain the model of the project.
	\item Implementation: This section is about the realization of the concepts and ideas development. It covers the implementation details like the modeling of the system, the tools and technologies used, different modules in the project, problems faced while implementing these modules and the algorithms being used for programming the problem
\end{itemize}

	