\chapter{Conclusion}
\section{ Applications}

The key features of LifeBlocks are the storage and sharing of records using IPFS and Smart Contracts deployed on the blockchain and the dynamic creation of Policy Smart Contracts. These features can find applications in various other fields.
The data sharing model using IPFS and Smart Contracts can be used for any tradeable asset such as :
\begin{enumerate}
\item Sharing energy credits or tokens in a decentralized smart grid
\item Maintaining and sharing of university records and transcripts
\item Monetization using limited time access in a music royalty program
\item Creating a unified KYC system
\end{enumerate}
The dynamic creation of Smart Contracts can be used for :
\begin{enumerate}
\item An escrow system for real estate.
\item Tokenization of any tangible asset
\end{enumerate}
\clearpage
\section{Conclusion \& Future Work}

This report presents LifeBlocks, a blockchain based insurance platform intended to replace the current archaic process of storing health records and the entire insurance policy life cycle i.e. from buying insurance to policy servicing to claim settlement. It aims to improve upon the current inefficiencies of the healthcare system resulting in improved quality of service for the citizens of India. By having a mechanism wherein users have to verify and link their Aadhaar card with their public address on the Blockchain we are providing an efficient alternative to the paper based KYC measures in use currently. We also provide storage of medical records in a secure and immutable manner so that the user does not have to worry about maintaining his paper trail of medical records and can securely share access to his records when needed. By allowing insurance directly market and sell insurance policies as smart contract to the user, it reduces operational cost of the company by cutting down on the middlemen involved in the system. In the future, the system can support automated claim settlements which requires deep domain knowledge to implement. Also as scalability and data retrieval problems inherent in the Blockchain ecosystem are being solved, the system can allow governments and pharmacies to run analytics on the data in the Blockchain to predict disease patterns and stocking up on medicines (inventory management).   


